Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-07-15 sports_analytics.Rmd
skeleton of competitions; #6
competitions and conferences
added repo URL

maybe some kaggle competitions (march madness, cite mike and greg's paper; and big data bowl)
-->

@@

>>>>

## Competitions

- Kaggle March Madness [@lopez2015building]
- Big Data Bowl
- Big Data Cup
- SABR Case competition

## Conferences

- NESSIS/CASSIS
- Sloan
- CMU
- UConn sports analytics

@@

The R Markdown file that generated this paper, including all R code, is available at <https://github.com/beanumber/wire21>.
